User-customized hashtag/tag prediction on Twitter and StackOverflow:\protect \\ Comparing vector-based and ACT-R memory models of tag retrieval

### 2013-10-10 writeups/proposal/proposal.tex
foo
Former-commit-id: 82bf16200aea676d7925092fc1395cbcdbf500c0 [formerly 17c8f537cde8542e193cf718c8131282192ff596]
Former-commit-id: c28162db69a154223350f3b6c8b4309603c65940

Co-occurrence-based modeling has been shown as a potentially useful approach when predicting Twitter hashtag use \parencite{Efron2010}.
Several memory retrieval models are based on this broad methodology, where a count is maintained of the times each contextual element (such as a word in a post) co-occur with a tag.
Two of the current state-of-the-art memory retrieval models are based on a co-occurrence methodology, and I'll be comparing these two models for hashtag prediction:
ACT-R's declarative memory retrieval theory and random permutation vector-based memory systems.

@@

The SNIF-ACT framework \parencites{Fu2007,Pirolli2003} is also based on the large-scale version of $S_{ji}$, and scales well when working with a large-scale search query database for internet search.

@@

A retrieval for a word following ``stack'' (``stack $\Phi$'') is done by creating a memory vector out of all information in context.
In this case, assume only a single piece of order information is available, that ``stack'' precedes the word to retrieve.
So the memory vector for context is the environment vector for one-back ``stack'' ($m_{C} = e_{stack^{-1}}$).
The memory vector for ``overflow'' ($m_{overflow}$) will be correlated the highest with this context vector ($m_{C}$) since ``overflow'' contains this vector.

>>>>

Co-occurrence-based modeling has been shown as a potentially useful approach when predicting Twitter hashtag use \parencite{Efron2010}.
Several memory retrieval models are based on this broad methodology, where a count is maintained of the times each contextual element (such as a word in a post) co-occur with a tag.
Two of the current state-of-the-art memory retrieval models are based on a co-occurrence methodology, and I'll be comparing these two models for hashtag prediction:
ACT-R's declarative memory (DM) retrieval theory and random permutation vector-based memory systems.

@@

The SNIF-ACT framework \parencites{Fu2007,Pirolli2003} is also based on the large-scale version of $S_{ji}$, and scaled well when working with a large-scale search query database for internet search.

@@

A resonance retrieval for a word following ``stack'' (``stack $\Phi$'') is done by creating a memory vector out of all information in context.
In this case, assume only a single piece of order information is available, that ``stack'' precedes the word to retrieve.
So the memory vector for context is the environment vector for one-back ``stack'' ($m_{C} = e_{stack^{-1}}$).
The memory vector for ``overflow'' ($m_{overflow}$) will be correlated the highest with this context vector ($m_{C}$) since ``overflow'' contains this vector.
